\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-22 trunk/intro.tex
Extra updates

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\texttt{T-REX}) an on-board adaptive control system that integrates
AI based planning and probabilistic state estimation in a hybrid
executive \cite{mcgann08a,mcgann08b,py10}.  Probabilistic state
estimation integrates a number of science observations to produce a
likelihood that the vehicle sensors perceive a feature of
interest. Onboard planning and execution enables adaptation of
navigation and instrument control based on the probability of having
detected such a phenomenon. It further enables goal-directed
commanding within the context of projected mission state and allows
for replanning for off-nominal situations and opportunistic science
events. The framework in addition to being used on an AUV, is general
enough be used for controlling a personal robot \cite{mcgann2009} and
is deployed on a European planetary rover testbed
\cite{goac11}. Probabilistic state estimation is discussed elsewhere
\cite{mcgann08d} and out of scope for this chapter. Deliberation and
reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's Dorado AUV shown in
Fig. \ref{fig:auv-fig}, which to the best of our knowledge is the only
operational marine platform anywhere being used for routine scientific
surveys with onboard plan synthesis.

@@

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section
\ref{sec:concepts}. \comment{add others} We conclude with Section
\ref{sec:conclusion}.

>>>>

We have developed, tested and deployed the Teleo-Reactive EXecutive
(\texttt{T-REX}) an on-board adaptive control system that integrates
AI based planning and %\sout{probabilistic} 
state estimation in a hybrid executive\cite{mcgann08a,mcgann08b,py10}. 
%  \sout{Probabilistic state estimation integrates a number of science observations to produce a
% likelihood that the vehicle sensors perceive a feature of
% interest}.\fcomment{\rx {\em does not} integrate probabilistic state
%   estimation! ... The HMM estimation was coded on top of \eu model but
%   neither \eu or \rx had explicit management of it} 
State estimation allow the system to keep track of the world evolution
as time advances based on a formal model distributed through the architecture.
Onboard planning and execution enables adaptation of
navigation and instrument control based on the state identified during
state estimation.
% \sout{the probability of having detected such a phenomenon} 
It further enables goal-directed
commanding within the context of projected mission state and allows
for replanning for off-nominal situations and opportunistic science
events. The framework in addition to being used on an AUV, is general
enough be used for controlling a personal robot \cite{mcgann2009} and
is deployed on a European planetary rover testbed
\cite{goac11}. While it is possible to integrate probabilistic
estimation on top of this framework \cite{mcgann08d}, such
representation is not explicitly handled by the framework and is
out of scope of this chapter.
% Probabilistic state estimation through modeling within 
% this framework can be done is discussed elsewhere
% \cite{mcgann08d} and out of scope for this chapter. 
Deliberation and reaction are integrated systematically over different temporal and
functional scopes within a single agent and a single model that covers
the needs of high-level mission management, low-level navigation,
instrument control, and detection of unstructured and poorly
understood phenomena. \rx is deployed on MBARI's Dorado AUV shown in
Fig. \ref{fig:auv-fig}, which to the best of our knowledge is the only
operational marine platform anywhere being used for routine scientific
surveys with onboard plan synthesis.

@@

This chapter is organized as follows. We start with some foundational
concepts in our Planning framework in Section~\ref{sec:concepts} which
includes a brief overview of AI Planning in
Section~\ref{sec:planningfound}. In Section~\ref{sec:basics} we go
deeper into the \eu framework itself, the basis of all deliberation
within \rx. A key portion is Section~\ref{sec:europa:pr} which details
the internal plan representation essential to planning within a
situated agent like \rx. Modeling (Section~\ref{sec:europa:modeling}),
Inference (Section~\ref{sec:europa:inference}) and Search
(Section~\ref{sec:europa:search}) further detail the important details
associated with \eu for the and relevant to how \rx works to the
reader. With these foundational elements out of the way, we transition
to \rx itself, in Section~\ref{sec:arch}, bring out architectural
details in Section~\ref{sec:arch:trex}, deal with the execution cycle
in Section~\ref{sec:arch:exec}, highlight how \rx deliberates in
Section~\ref{sec:arch:europa} finally delving deeper into the key
concept of synchronization in Section~\ref{sec:arch:synch}. Further
details on deliberation within \rx (Section~\ref{sec:arch:plan}) and
how planning and execution are interleaved are shown in
Section~\ref{sec:arch:intertwine}. We offer results from our
experiments at sea in Section~\ref{sec:results}, offer some insights
into the near-term future goals of our research in
Section~\ref{sec:future} and conclude with
Section~\ref{sec:conclusion}.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "setobook"
%%% End:
